Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
half(-)canonical -> spin canonical

The pairs $(\sx, \Delta)$ are called \textbf{log stacky curves}
and the study of their canonical rings is the main focus of
the work by Voight and Zureick-Brown \cite{vzb:stacky}.
For this paper, we consider \textbf{log spin curves} which are
triples $(\sx, \Delta, \halfcan)$ where $\Delta$ is a log divisor
and a divisor $\halfcan$ which satisfies the property that
$2\halfcan \sim K_\sx + \Delta$. Such a divisor $\halfcan$
is called a \textbf{half-canonical divisor} on $(\sx, \Delta)$
and are sometimes referred to as theta-characteristics in other
literature. We also use $\halfcan_X$ to refer to the half-canonical
divisor associated with the coarse space $X$ of $\sx$, i.e.
$\halfcan_X$ is a divisor such that $2\halfcan \sim K_X$.
Furthermore, we use the following analogous notations:

@@

\section{Inductive Lemmas}
\label{sec:induction}
First we present several lemmas which provide the
inductive steps for the proof of the main theorem: Theorem
~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
	which determine the generators and relations of $R_\halfcan=R_{\halfcan' + \frac{\alpha
}{\beta}P}$ from those of $R_{\halfcan'}$, where
%where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
$\halfcan' \in \di
X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ$. 
In
Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log half canonical ring of a curve with signature $(g; e_1', 
\ldots, e_\tau'; 0)$ to that of a
curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$. \todo{Peter: I tried to edit this, but I can't figure out how to make this sentence work well.  There are too many clauses...}
%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
%half-canonical divisors.

@@

\ssec{Adding Points}  \todo{Peter: Note to self: replace $H^0(X, \lfloor L\rfloor)$ with $H^0(\sx, L)$.}
\label{ssec:add-points}
%In this section, we prove various inductive statements under the following setup:
%Let $\halfcan' \in \di \BQ \otimes X$ be $\BQ$-divisor of $X$ (and often a log half-canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions. Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.  Then we will explicitly describe elements that generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis). \todo{Aaron: What new ideas does this description add that wasn't already described in the previous paragraph? Also, in general it's a good idea to be specific about what the most important lemmas are in the section, although I also added this to the general description of section 3.}
\todo{Pervasive change: Make sure all $\initial(I)$ are written as $\initial(I)$. We can even build this in to the macro possibly? }
Before proving three lemmas that allow us to inductively add points to the support of a divisor, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.  This criterion will be used repeatedly to show that a given homogeneous ideal is in fact the ideal of relations.

@@

\begin{lem}
\label{lem:sat-3}
Suppose $L'$ is a log half-canonical divisor of $\sx'$ with coarse
space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ and $R_
{\halfcan'} \cong k[x_3, x_4 , x_5, \ldots, x_m]/I'$. Choose $x_3, \ldots, x_m$ such that $-\ord^{L'}_P(x_i)=0$ for all $i,$ which is possible as $X$ has genus $0$. Let $L = L' + \frac
{1}{3}P$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that
the ordering on $k[x_3, \ldots, x_m]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}

@@

%Since $\halfcan$ is a half canonical divisor, 

@@

\section{High Genus}
\label{sec:g_high}
We now consider the case when the genus is at least 2. In this case, we are able to bound the degrees and relations of the half canonical ring $R_L$. In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Section ~\ref{sec:g_1} and Section ~\ref{sec:g_0} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively. The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved, while in this section we will be able to appeal to general theory.

@@

\begin{rem}
\label{rem:relations_generation_ten}
In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L=P$ is a half canonical divisor on a genus 2 curve, then $R_L$ has a relation in degree 10. Therefore, the bound from Proposition ~\ref{prop:relation_11}, that $I_L$ is generated in degree at most 11 if $\Delta = 0$ and at most $10$ if $\Delta > 0,$ is close to sharp.
\end{rem}

@@

The inductive strategy we will adopt to prove Theorem ~\ref{thm:main} is similar to that of the genus $g \geq 2$ case. In the case of a genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P - Q$ where $P,Q$ are distinct points, fixed  under the hyperelliptic involution. We aim to inductively construct presentations by increasing the values of the $e_i$ using Lemma ~\ref{lem:raise-stacky-order} and add additional points using Lemma ~\ref{lem:sat-1} and Lemma ~\ref{lem:sat-2}.

@@

\begin{example}
\label{eg:exception-1-5}
Let $L' = P - Q + \frac{2}{5}P_1$ be a half canonical divisor on a stacky curve $\sx$. Let $u \in (P_L)_1$ be any nonzero element. We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element. We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$. Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_{P_1} = -P_1$. Then, we claim there is some $\alpha \in k$ so that
$R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha uy_5^2).$

@@

\begin{enumerate}
	\item In the case $g \geq 2$, Proposition ~\ref{prop:relation_11} gives a bound on the degree of generators of the relations of a log spin canonical ring $R_L$. Additionally, by Remark ~\ref{rem:relations_generation_ten}, any curve of genus 2 with half canonical divisor $L = P$ has spin canonical ring $R_L$ with relations in degree 10. This raises the question of whether the bound of 11 on the degree of the relations in $R_L$ can be reduced to $10$. In particular, we make the following conjecture.
\begin{conjecture}
\label{conj:relations-10}
If $X$ is a curve of genus $g \geq 2$ and $L \in \di X$ with $2L \sim K,$ the ideal of relations in $R_L$ is generated in degree at most $10$. More precisely, if $x_1,\ldots, x_n$ is a minimal set of generators for $R_L$ and $\phi:k[y_1,\ldots, y_n] \rightarrow R_L, y_i \mapsto x_i,$ then $I_L := \ker \phi$, is generated in degree at most 10. 
\end{conjecture}
Note that in the case $\dim L \geq 2$ and $L$ is basepoint-free, by Neves ~\cite[Proposition III.12]{neves:halfcan}, $I_L$ is generated in degree at most 8. Additionally, if Conjecture ~\ref{conj:relations-10} were true, by Theorem ~\ref{thm:main} we would immediately obtain the following corollary, providing a more concise statement than that of Theorem ~\ref{thm:main}.
\begin{cor}
\label{cor:main-refined}
Let $(\sx,\Delta,L)$ be a log spin curve over a perfect field $k$ with signature $(g;e_1,\ldots, e_r;\delta)$ and let $R_L$ be the log canonical ring. Suppose Conjecture ~\ref{conj:relations-10}. Then, $R_L$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e,$ apart from a finite list of exceptions.
\end{cor}
	\item Another direction for further research is to extend the results of this paper to divisors $D \in \di \sx$ on a stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such divisors would translate to rings of fractional weight modular forms. As defined in Adler and Ramanan, immediately following \cite[Corollary 24.5]{adler:moduli}, a {\bf modular form of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a line bundle $\eta$ so that there exists a line bundle $\gamma$ with $\gamma^{\otimes a} \cong \eta$ and $\gamma^{n} \cong \Omega_{X(p)}^1$. Adler and Ramanan \cite[Appendix 2]{adler:moduli} construct an explicit basis of weight $\frac{4}{5}$ modular forms for $X(11)$. Fractional modular forms also make an apperance in Milnor \cite[$\mathsection$ 6]{milnor:fractional-weight}. In this work, Milnor shows that for a triangle group $\Gamma$ of signature $(0; e_1,e_2,e_3; 0)$ there exist generators $f_1,f_2,f_3$ of a certain ring of fractional weight modular forms, satisfying $f_1^{e_1}+f_2^{e_2}+f_3^{e_3} = 0$.

@@

\begin{question}
\label{ques:fractional-weight}
If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K,$ where $K$ is the canonical divisor of $\sx$, can one bound the degrees of generators and relations of $R_D$?
\end{question}
Note that that the above question is answered affirmatively in the case that $\sx$ has genus $0$ and $D$ is effective, as follows by inductively applying Lemma ~\ref{lem:sat-1}: If $\sx$ has signature $(g;e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most $2e$. Additionally, it may be possible to modify the proof of Lemma ~\ref{lem:raise-stacky-order} to extend to the setting of fractional weight modular forms. Given suitable generalizations of these lemmas, one may be able to approach the problem of finding generators and relations for fractional weight modular forms using techniques similar to those in this paper.
	\item In Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky}, the notion of a generic initial ideal is defined, which encapsulates the idea of whether the relations for $R_L$ are generically chosen, in a precise sense. The proof of Theorem ~\ref{thm:main} decidedly does not yield a generic initial ideal, as generators and relations are constructed in a highly nongeneric manner. In particular, Lemma ~\ref{lem:raise-stacky-order} constructs generators with non-maximal pole orders at certain points, making the relations non-generic. 
\begin{question}
\label{ques:generic-initial}
If $(\sx,\Delta,L)$ is a log spin curve with signature $\sigma$, does there exist a function $\sigma \mapsto d(\sigma)$ so that the generic initial ideal {\rm(} with some specified ordering{\rm)} is generated in degree at most $d(\sigma)$? Can one write down the generic initial ideal explicitly?
\end{question}
	\item As noted in Remark ~\ref{rem:explicit-generators}, the proof of Theorem ~\ref{thm:main} given in this paper gives an explicit procedure for computing the generators and relations of $R_L$ when the genus of $\sx$ is $0$ or $1$.
\begin{question}
\label{ques:algorithm}
Can one give an algorithm for explicitly computing the generators and relations for an arbitrary genus $g \geq 2$ curve?
\end{question}
Suppose the generators and relations of $R_{L_X}$ are known, where $(\sx, \Delta, L)$ is a spin canonical ring, $X$ is the coarse space of $\sx$, and $L_X \leq L$ is a half canonical divisor of $X$. In this case our proof of Theorem ~\ref{thm:main} yields an algorithm for determining the generators of $L$. This raises the following Petri-like question:
\begin{question}
\label{ques:half-canonical-petri}
Given a {\rm(}non-stacky {\rm)} curve $X$ and a half canonical divisor $L \in \di X$, can one write down a set of minimal generators and minimal relations for $R_L$? If so, can one give the generic ideal of $R_L$ or the generic initial ideal of $R_L$, as defined in Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky}?
\end{question}
In particular, if Question ~\ref{ques:half-canonical-petri} were answered affirmatively one would be able to write down explicit generators and relations for $R_L$ on a stacky curve, essentially by inductively applying Lemma ~\ref{lem:raise-stacky-order}.
	\todo{This last one doesn't seem particularly interesting. Should we remove it?}
	\item While Theorem ~\ref{thm:main} gives a minimal set of generators for the log spin canonical ring $R_L,$ the set of relations is not minimal. In many of the $g = 0$ and $g=1$ cases, it is not too difficult to see that our inductive procedure also yields a minimal set of relations for $R_L$. One might investigate whether the generators and relations given by the inductive proof of Theorem ~\ref{thm:main} are always minimal.
	\end{enumerate}

>>>>

The pairs $(\sx, \Delta)$ are called \textbf{log stacky curves}
and the study of their canonical rings is the main focus of
the work by Voight and Zureick-Brown \cite{vzb:stacky}.
For this paper, we consider \textbf{log spin curves} which are
triples $(\sx, \Delta, \halfcan)$ where $\Delta$ is a log divisor
and a divisor $\halfcan$ which satisfies the property that
$2\halfcan \sim K_\sx + \Delta$. Such a divisor $\halfcan$
is called a \textbf{spin canonical divisor} on $(\sx, \Delta)$
and are sometimes referred to as theta-characteristics in other
literature. We also use $\halfcan_X$ to refer to the spin canonical
divisor (also known as the half-canonical divisor or semi-canonical
divisor) associated with the coarse space $X$ of $\sx$, i.e.
$\halfcan_X$ is a divisor such that $2\halfcan \sim K_X$.
Furthermore, we use the following analogous notations:

@@

\section{Inductive Lemmas}
\label{sec:induction}
First we present several lemmas which provide the
inductive steps for the proof of the main theorem: Theorem
~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove three lemmas
%Lemma ~\ref {lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3}
	which determine the generators and relations of $R_\halfcan=R_{\halfcan' + \frac{\alpha
}{\beta}P}$ from those of $R_{\halfcan'}$, where
%where $X$ is a curve, \todo{Peter: I don't think we need to include this instantiation; $X$ always represents a curve throughout the paper, and we should say something to that effect in the background}
$\halfcan' \in \di
X \otimes \BQ $ and  $\frac{\alpha}{\beta} \in \BQ$. 
In
Subsection ~\ref{ssec:raise-orders}, we prove a inductive lemma allowing us to transfer information about the log spin canonical ring of a curve with signature $(g; e_1', 
\ldots, e_\tau'; 0)$ to that of a
curve with the same log divisor, the same stacky points, and some subset of the $e_ i'$ incremented by $2$. \todo{Peter: I tried to edit this, but I can't figure out how to make this sentence work well.  There are too many clauses...}
%While Lemma ~\ref{lem:sat-1} may be applied in a fairly general 
%context, Lemma ~\ref{lem:raise-stacky-order} is more specific to 
%spin canonical divisors.

@@

\ssec{Adding Points}  \todo{Peter: Note to self: replace $H^0(X, \lfloor L\rfloor)$ with $H^0(\sx, L)$.}
\label{ssec:add-points}
%In this section, we prove various inductive statements under the following setup:
%Let $\halfcan' \in \di \BQ \otimes X$ be $\BQ$-divisor of $X$ (and often a log spin canonical divisor of some $\sx'$), satisfying certain conditions about $\deg(\lfloor d \halfcan'\rfloor)$ for various values of $d\in\mathbb{N}$ and certain saturation conditions. Let $\halfcan=\halfcan'+P$ for some $P$ possibly in the support of $\halfcan$.  Then we will explicitly describe elements that generate $R_\halfcan$ over $\halfcan$' and initial terms of relations that generate $\initial(I')$ over $\initial(I)$ (allowing the construction of a corresponding Gr\"{o}bner Basis). \todo{Aaron: What new ideas does this description add that wasn't already described in the previous paragraph? Also, in general it's a good idea to be specific about what the most important lemmas are in the section, although I also added this to the general description of section 3.}
\todo{Pervasive change: Make sure all $\initial(I)$ are written as $\initial(I)$. We can even build this in to the macro possibly? }
Before proving three lemmas that allow us to inductively add points to the support of a divisor, we give a criterion to determine if a set of monomials generates the initial ideal of relations of $k[x_1, \ldots, x_m]\to R_D$.  This criterion will be used repeatedly to show that a given homogeneous ideal is in fact the ideal of relations.

@@

\begin{lem}
\label{lem:sat-3}
Suppose $L'$ is a log spin canonical divisor of $\sx'$ with coarse
space $X$ of genus 0 such that $\sat(\Eff(\halfcan')) = 3$ and $R_
{\halfcan'} \cong k[x_3, x_4 , x_5, \ldots, x_m]/I'$. Choose $x_3, \ldots, x_m$ such that $-\ord^{L'}_P(x_i)=0$ for all $i,$ which is possible as $X$ has genus $0$. Let $L = L' + \frac
{1}{3}P$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that
the ordering on $k[x_3, \ldots, x_m]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}

@@

%Since $\halfcan$ is a spin canonical divisor, 

@@

\section{High Genus}
\label{sec:g_high}
We now consider the case when the genus is at least 2. In this case, we are able to bound the degrees and relations of the spin canonical ring $R_L$. In this section, we do not obtain explicit presentations of $R_L.$ In contrast, in Section ~\ref{sec:g_1} and Section ~\ref{sec:g_0} we will not only obtain bounds on the generators and relations, but also obtain presentations inductively. The tradeoff is that in the cases of genus 0 and 1, we will have to explicitly deal with base cases, making the induction more involved, while in this section we will be able to appeal to general theory.

@@

\begin{rem}
\label{rem:relations_generation_ten}
In \cite{neves:halfcan}[Theorem III.19], Neves shows that if $L = P$
 is a spin canonical divisor on a genus 2 curve, then $R_L$ has a
relation in degree 10. Therefore, the bound from Proposition
~\ref{prop:relation_11}, that $I_L$ is generated in degree at most
11 if $\Delta = 0$ and at most $10$ if $\Delta > 0,$ is close to
sharp.
\end{rem}

@@

The inductive strategy we will adopt to prove Theorem ~\ref{thm:main} is similar to that of the genus $g \geq 2$ case. In the case of a genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for spin canonical divisors are $\halfcan' = 0$ or $\halfcan' = P - Q$ where $P,Q$ are distinct points, fixed  under the hyperelliptic involution. We aim to inductively construct presentations by increasing the values of the $e_i$ using Lemma ~\ref{lem:raise-stacky-order} and add additional points using Lemma ~\ref{lem:sat-1} and Lemma ~\ref{lem:sat-2}.

@@

\begin{example}
\label{eg:exception-1-5}
Let $L' = P - Q + \frac{2}{5}P_1$ be a spin canonical divisor on a stacky curve $\sx$. Let $u \in (P_L)_1$ be any nonzero element. We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element. We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$. Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_{P_1} = -P_1$. Then, we claim there is some $\alpha \in k$ so that
$R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha uy_5^2).$

@@

\begin{enumerate}
	\item In the case $g \geq 2$, Proposition ~\ref{prop:relation_11} gives a bound on the degree of generators of the relations of a log spin canonical ring $R_L$. Additionally, by Remark ~\ref{rem:relations_generation_ten}, any curve of genus 2 with spin canonical divisor $L = P$ has spin canonical ring $R_L$ with relations in degree 10. This raises the question of whether the bound of 11 on the degree of the relations in $R_L$ can be reduced to $10$. In particular, we make the following conjecture.
\begin{conjecture}
\label{conj:relations-10}
If $X$ is a curve of genus $g \geq 2$ and $L \in \di X$ with $2L \sim K,$ the ideal of relations in $R_L$ is generated in degree at most $10$. More precisely, if $x_1,\ldots, x_n$ is a minimal set of generators for $R_L$ and $\phi:k[y_1,\ldots, y_n] \rightarrow R_L, y_i \mapsto x_i,$ then $I_L := \ker \phi$, is generated in degree at most 10. 
\end{conjecture}
Note that in the case $\dim L \geq 2$ and $L$ is basepoint-free, by Neves ~\cite[Proposition III.12]{neves:halfcan}, $I_L$ is generated in degree at most 8. Additionally, if Conjecture ~\ref{conj:relations-10} were true, by Theorem ~\ref{thm:main} we would immediately obtain the following corollary, providing a more concise statement than that of Theorem ~\ref{thm:main}.
\begin{cor}
\label{cor:main-refined}
Let $(\sx,\Delta,L)$ be a log spin curve over a perfect field $k$ with signature $(g;e_1,\ldots, e_r;\delta)$ and let $R_L$ be the log canonical ring. Suppose Conjecture ~\ref{conj:relations-10}. Then, $R_L$ is generated in degree at most $e = \max(5,e_1,\ldots, e_r)$ with relations in degree at most $2e,$ apart from a finite list of exceptions.
\end{cor}
	\item Another direction for further research is to extend the results of this paper to divisors $D \in \di \sx$ on a stacky curve $\sx,$ where $nD \sim K.$ The canonical rings of such divisors would translate to rings of fractional weight modular forms. As defined in Adler and Ramanan, immediately following \cite[Corollary 24.5]{adler:moduli}, a {\bf modular form of fractional weight} $\frac{2a}{n}$ on $X(p)$ is a section of a line bundle $\eta$ so that there exists a line bundle $\gamma$ with $\gamma^{\otimes a} \cong \eta$ and $\gamma^{n} \cong \Omega_{X(p)}^1$. Adler and Ramanan \cite[Appendix 2]{adler:moduli} construct an explicit basis of weight $\frac{4}{5}$ modular forms for $X(11)$. Fractional modular forms also make an apperance in Milnor \cite[$\mathsection$ 6]{milnor:fractional-weight}. In this work, Milnor shows that for a triangle group $\Gamma$ of signature $(0; e_1,e_2,e_3; 0)$ there exist generators $f_1,f_2,f_3$ of a certain ring of fractional weight modular forms, satisfying $f_1^{e_1}+f_2^{e_2}+f_3^{e_3} = 0$.

@@

\begin{question}
\label{ques:fractional-weight}
If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K,$ where $K$ is the canonical divisor of $\sx$, can one bound the degrees of generators and relations of $R_D$?
\end{question}
Note that that the above question is answered affirmatively in the case that $\sx$ has genus $0$ and $D$ is effective, as follows by inductively applying Lemma ~\ref{lem:sat-1}: If $\sx$ has signature $(g;e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most $2e$. Additionally, it may be possible to modify the proof of Lemma ~\ref{lem:raise-stacky-order} to extend to the setting of fractional weight modular forms. Given suitable generalizations of these lemmas, one may be able to approach the problem of finding generators and relations for fractional weight modular forms using techniques similar to those in this paper.
	\item In Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky}, the notion of a generic initial ideal is defined, which encapsulates the idea of whether the relations for $R_L$ are generically chosen, in a precise sense. The proof of Theorem ~\ref{thm:main} decidedly does not yield a generic initial ideal, as generators and relations are constructed in a highly nongeneric manner. In particular, Lemma ~\ref{lem:raise-stacky-order} constructs generators with non-maximal pole orders at certain points, making the relations non-generic. 
\begin{question}
\label{ques:generic-initial}
If $(\sx,\Delta,L)$ is a log spin curve with signature $\sigma$, does there exist a function $\sigma \mapsto d(\sigma)$ so that the generic initial ideal {\rm(} with some specified ordering{\rm)} is generated in degree at most $d(\sigma)$? Can one write down the generic initial ideal explicitly?
\end{question}
	\item As noted in Remark ~\ref{rem:explicit-generators}, the proof of Theorem ~\ref{thm:main} given in this paper gives an explicit procedure for computing the generators and relations of $R_L$ when the genus of $\sx$ is $0$ or $1$.
\begin{question}
\label{ques:algorithm}
Can one give an algorithm for explicitly computing the generators and relations for an arbitrary genus $g \geq 2$ curve?
\end{question}
Suppose the generators and relations of $R_{L_X}$ are known, where $(\sx, \Delta, L)$ is a spin canonical ring, $X$ is the coarse space of $\sx$, and $L_X \leq L$ is a spin canonical divisor of $X$. In this case our proof of Theorem ~\ref{thm:main} yields an algorithm for determining the generators of $L$. This raises the following Petri-like question:
\begin{question}
\label{ques:spin-canonical-petri}
Given a {\rm(}non-stacky {\rm)} curve $X$ and a spin canonical divisor $L \in \di X$, can one write down a set of minimal generators and minimal relations for $R_L$? If so, can one give the generic ideal of $R_L$ or the generic initial ideal of $R_L$, as defined in Voight and Zureick Brown \cite[Definition 2.2.7]{vzb:stacky}?
\end{question}
In particular, if Question ~\ref{ques:spin-canonical-petri} were answered affirmatively one would be able to write down explicit generators and relations for $R_L$ on a stacky curve, essentially by inductively applying Lemma ~\ref{lem:raise-stacky-order}.
	\todo{This last one doesn't seem particularly interesting. Should we remove it?}
	\item While Theorem ~\ref{thm:main} gives a minimal set of generators for the log spin canonical ring $R_L,$ the set of relations is not minimal. In many of the $g = 0$ and $g=1$ cases, it is not too difficult to see that our inductive procedure also yields a minimal set of relations for $R_L$. One might investigate whether the generators and relations given by the inductive proof of Theorem ~\ref{thm:main} are always minimal.
	\end{enumerate}
